Online Tuning of EASY-Backfilling using Queue Reordering Policies.

### 2018-03-13 paper/paper.tex
last version.

\author{
\IEEEauthorblockN{Eric Gaussier}\\
\IEEEauthorblockA{Univ. Grenoble Alpes, CNRS, Grenoble INP, LIG\\
  eric.gaussier@imag.fr } \\
\IEEEauthorblockN{J\'er\^ome Lelong}\\
\IEEEauthorblockA{Univ. Grenoble Alpes, Inria, CNRS, Grenoble INP, LJK\\
jerome.lelong@imag.fr}  \\
\IEEEauthorblockN{Valentin Reis, Denis Trystram}\\
\IEEEauthorblockA{Univ. Grenoble Alpes, Inria, CNRS, Grenoble INP, LIG\\
denis.trystram@imag.fr}
}
\begin{document}

@@

>>>>

\author{
\IEEEauthorblockN{Eric Gaussier}\\
\IEEEauthorblockA{Univ. Grenoble Alpes, CNRS, Grenoble INP, LIG\\
  eric.gaussier@imag.fr } \\
\IEEEauthorblockN{J\'er\^ome Lelong}\\
\IEEEauthorblockA{Univ. Grenoble Alpes, Inria, CNRS, Grenoble INP, LJK\\
jerome.lelong@imag.fr}  \\
\IEEEauthorblockN{Valentin Reis}\\
\IEEEauthorblockA{Univ. Grenoble Alpes, Inria, CNRS, Grenoble INP, LIG\\
valentin.reis@imag.fr}\\
\IEEEauthorblockN{Denis Trystram,~\IEEEmembership{Senior Member,~IEEE,}}\\
\IEEEauthorblockA{Univ. Grenoble Alpes, Inria, CNRS, Grenoble INP, LIG\\
denis.trystram@imag.fr}
}
\begin{document}

\IEEEtitleabstractindextext{D.4.7.f Parallel Systems, D.4.1.e Scheduling, I.2.6 Learning}

@@

\begin{IEEEbiography}[{\includegraphics[width=1in,height=1.25in,clip,keepaspectratio]{figures/eric}}]{Eric Gaussier}
Prof. Eric Gaussier is known for his work on the intersection of Artificial
Intelligence (AI) and Data Science (DS), in particular for his contributions on
models and alogrithms to extract information, insights and knowledge from
texts. He has worked on three main subfields of AI and DS: machine learning,
information retrieval and computational linguistics. He is also interested in
modeling how textual information is shared in social content networks, and how
such networks evolve over time. More recently, he has also been working on
improving job scheduling techniques through machine learning, and in learning
representations for different types of sequences, as texts and time series. He
currently is Director of the Laboratory of Informatics in Grenoble (LIG).
\end{IEEEbiography}

\begin{IEEEbiography}[{\includegraphics[width=1in,height=1.25in,clip,keepaspectratio]{figures/jerome}}]{J\'er\^ome Lelong}
Jérôme Lelong is an associate professor at Grenoble Institute of Technology and
member of the LJK laboratory. Since 2011, he has been the head of the master
program on financial engineering. He is a specialist of stochastic
optimization and HPC algorithms for learning. He has studied many application
going from quantitative finance to rare event simulation for electronic
circuit design.
\end{IEEEbiography}

\begin{IEEEbiography}[{\includegraphics[width=1in,height=1.25in,clip,keepaspectratio]{figures/valentin}}]{Valentin Reis}
Valentin is a PhD candidate at Inria/University Grenoble Alpes, France.  He is
currently working on using learning to improve scheduling processes in
high performance computing. He is broadly interested in machine learning and
functionnal programming.
\end{IEEEbiography}

\begin{IEEEbiography}[{\includegraphics[width=1in,height=1.25in,clip,keepaspectratio]{figures/denis}}]{Denis Trystram}
Denis Trystram is distinguished professor in the institute of technology of
Univ. Grenoble-Alpes. He is an honorary member of the prestigious Institut
Universitaire de France. He was vice-director of the LIG in Grenoble for 2
years (2014-2015) where he is leading a research group on resource management
for parallel and distributed systems in a joint team with Inria. Since 2010, he
is director of the international Master program in Computer Science at Univ.
Grenoble-Alpes. He is a well-known specialist of scheduling in the broad
variety of parallel and distributed platforms (including HPC clusters, clouds,
Internet of Things) and multi-objective optimization (in particular with a
focus on energy). Currently, he is interested in learning and its link with
resource management.
\end{IEEEbiography}
